---
title: "Neighbourhood richness to Recovery correlation"
output: html_notebook
---

# June 15 2023
# Systematically get the correlation between recovery and abundance at baseline
# and correlate that with neighbourhood richness


# Load in libraries
```{r}
suppressWarnings(suppressMessages(library("readr")))
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(umap)))
```

# Bring in neighborhood analysis by importing affinity matrixes
```{r}
## Bring data in by FOV 
studylist <- c("3402_CECUM", "3402_COLON", "3405_CECUM", "3405_COLON", "3406_CECUM", "3406_COLON", "3407_CECUM", "3407_COLON", "3409_CECUM", "3409_COLON", "3412_CECUM", "3412_COLON", "3413_CECUM", "3413_COLON", "3414_CECUM", "3414_COLON", "3415_CECUM", "3415_COLON", "3422_CECUM", "3422_COLON", "3423_CECUM", "3423_COLON", "3424_CECUM", "3424_COLON", "3428_CECUM", "3428_COLON", "3429_CECUM", "3429_COLON", "3430_CECUM", "3430_COLON", "3434_CECUM", "3434_COLON", "3435_CECUM", "3435_COLON", "3436_CECUM", "3436_COLON", "3438_CECUM", "3438_COLON", "3441_CECUM", "3441_COLON", "3442_CECUM", "3442_COLON", "3446_CECUM", "3446_COLON", "3447_CECUM", "3447_COLON", "3448_CECUM", "3448_COLON", "3451_CECUM", "3451_COLON", "3452_CECUM", "3452_COLON", "3454_CECUM", "3454_COLON" )

df.list <- list()
for (i in 1:length(studylist))  {
all.files <- list.files(paste0('../data/BugCountsR5_Mar242023/', studylist[i], "/radius_5/"))  
all.files <- grep("affinity_ratio_matrix_rep", all.files, value = TRUE) 
file.df <- tibble(filename = all.files)
file.df.paths <- file.df %>% mutate(filepath = paste0('../data/BugCountsR5_Mar242023/', studylist[i], "/radius_5/", filename))
file.df.paths$study <- studylist[i]
df.list[[i]] <- file.df.paths # add it to your list
}

df.list.all <- do.call(rbind, df.list)
df.list.all

read.csv.and.add.filename <- function(filepath){
  interim1 <- read_csv(filepath) %>%
    mutate(filepath=filepath)  # adds a column with the filepath
  colnames(interim1)[1] <- "Center_Bug" #change the name of the first column
  interim1
}

# for each file, read the csv, and filename as column
raw.data <- lapply(df.list.all$filepath, read.csv.and.add.filename) %>% bind_rows() 

## add in column for mouse, location, tissue_replicate, and FOV
raw.data.wide <- raw.data %>% mutate(Mouse = str_sub(filepath, 37, 40)) %>% mutate(Tissue = str_sub(filepath, 42, 46)) %>%
  mutate(Section = str_sub(filepath, 83, 83)) %>% mutate(FoV = str_sub(filepath, 89, 89))

 
# import tissue metadata
md <- read.csv("../data/Tissues_Metadata.csv")
#shorten metadata to only include samples we sent (3 mice per group)
mouse <- c("3402", "3405", "3406" , "3407", "3409", "3412", "3413", "3414", "3415", "3422", "3423", "3424", "3428", "3429", "3430", "3434", "3435", "3436", "3438", "3441", "3442", "3446", "3447", "3448", "3451", "3452", "3454")

# clean up the metadata to only include rows for the mice we submitted to kanvas
md.images <- md[,1:4] %>% filter (Mouse %in% mouse)
md.images$Mouse <- as.character(md.images$Mouse)

Affinity.wide <- left_join(raw.data.wide, md.images, by = "Mouse")
```

# Turn Affinity.wide to Affinity.long
```{r}
#turn column names into character
# colnames(Affinity.wide) <- as.character(colnames(Affinity.wide))
# 
# excluded_vars <- c("Mouse", "Tissue", "Section", "FoV", "Treatment", "Cage", "Day", "filepath")
# 
# long.Center <- select(Affinity.wide, -any_of(excluded_vars)) %>% 
#   pivot_longer(-Center_Bug, names_to = "Bug_in_Hood", values_to = "Affinity_Score", names_prefix = "Bug_") 
# 
# excluded_vars <- c("Mouse", "Tissue", "Section", "FoV", "Treatment", "Cage", "Day", "Center_Bug")
# 
# long.filepath <- select(Affinity.wide, -any_of(excluded_vars)) %>% 
#   pivot_longer(-filepath, names_to = "Bug_in_Hood", values_to = "Affinity_Score", names_prefix = "Bug_") 
# identical(long.Center$Affinity_Score, long.filepath$Affinity_Score) 
# identical(long.Center$Bug_in_Hood, long.filepath$Bug_in_Hood) 
# 
# Affinity.long <- cbind(long.Center, long.filepath)[,1:4]

Affinity.long <- Affinity.wide %>% dplyr::select(-filepath) %>% 
  pivot_longer(cols = 2:64, names_to = "Bug_in_Hood", values_to = "Affinity_Score", names_prefix = "Bug_" )

# Add in Bug names
Affinity.long$Bug_in_Hood <- Affinity.long$Bug_in_Hood %>% as.numeric() %>% round(digits = 0) %>% as.character()
ASV <- read.csv("../data/asv_lineage_abundance.csv")

ASV$ASV_Cluster_ID <- as.character(ASV$ASV_Cluster_ID)
Affinity.long <- left_join(Affinity.long, ASV, by = c("Bug_in_Hood" = "ASV_Cluster_ID"))

Affinity.long$Sample <- paste(Affinity.long$Treatment, Affinity.long$Day, Affinity.long$Tissue, 
                                Affinity.long$Mouse, Affinity.long$Section, Affinity.long$FoV, sep = "_") 
```

# Figure 5A
```{r}
set.seed(27)

BUGID <- 30 #Ligilacto murinis

# Filter for your bug
OneBug <- Affinity.long %>% filter(Center_Bug == BUGID)

# sample by feature matrix
OneBug.wide <- OneBug %>% dplyr::select(Affinity_Score, ASV_Cluster_Scientific_Name, Sample) %>% 
  pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score)

# NAs come from not existing in the affinity matrix, so it can be replaced with 0
OneBug.wide[is.na(OneBug.wide)] <- 0

# OneBug$Sample <- paste(OneBug$Treatment, OneBug$Day, OneBug$Tissue, OneBug$Mouse, OneBug$Section, OneBug$FoV, sep = "_")
umap.affinity <- umap(column_to_rownames(OneBug.wide, "Sample"), n_neighbors = 10)

# get metadata
labels <- OneBug %>% dplyr::select(ASV_Cluster_Scientific_Name, Sample, Tissue, Treatment, Day, Affinity_Score) %>% 
  pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score) %>% .[,1:4] 
#add row numbers as ID
labels$ID <- 1:dim(labels)[1]


umap_df <- umap.affinity$layout %>%
  as.data.frame()%>%
  rename(UMAP1="V1",
         UMAP2="V2") %>%
  mutate(ID = row_number())%>%
  left_join(labels, by="ID")

# fix treatment names 
umap_df$Treatment <- gsub("H2O", "Water", umap_df$Treatment)
umap_df$Treatment <- as.factor(umap_df$Treatment)
umap_df$Treatment <- factor(umap_df$Treatment, levels = c("Water", "Ampicillin", "Vancomycin"))

umap_df %>%
  ggplot(aes(x = UMAP1, y = UMAP2, color = as.character(Day) ))+
  geom_point(size = 2, aes(shape = Treatment)) +
  facet_wrap(~Tissue) +
  #stat_ellipse(type = "t") +
  theme(text = element_text(size = 18)) +
  labs(x = "UMAP1",
       y = "UMAP2",
      title = "L. murinis") +
  scale_shape_manual(values=c(1,2,3))


#ggsave("../Figures/Spatial/RC_30_UMAP.pdf", width = 8, height = 6)
```

# FIGURE 5B
```{r}
# Filter
OneBug.wide.Van.Cecum <- OneBug %>% filter(Tissue == "CECUM", Treatment == "Vancomycin") %>% 
  dplyr::select(ASV_Cluster_Scientific_Name, Sample, Affinity_Score) %>% pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score)

# Change NA to 0 (NAs come from not existing in the affinity matrix)
OneBug.wide.Van.Cecum[is.na(OneBug.wide.Van.Cecum)] <- 0
OneBug.wide.Van.Cecum <- OneBug.wide.Van.Cecum %>% column_to_rownames("Sample")

#Make NMDS
NMDS3 <- metaMDS(OneBug.wide.Van.Cecum, k = 2, trymax = 100, trace = F, autotransform = FALSE, distance="bray")

# get sample metadata 
OneBug.wide.Van.Cecum.md <- OneBug %>% filter(Tissue == "CECUM", Treatment == "Vancomycin") %>% 
  dplyr::select(ASV_Cluster_Scientific_Name, Sample, Affinity_Score, Treatment, Tissue, Day) %>% pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score) %>% .[1:4]

biplot.df1 <- scores(NMDS3)$sites %>% as_tibble(rownames = "Sample") %>%
  left_join(OneBug.wide.Van.Cecum.md, by = "Sample" ) %>% dplyr::select(Sample, NMDS1, NMDS2)

biplot.df1$Score <- "Site"
colnames(biplot.df1)[1] <- "Label"

biplot.df2 <- scores(NMDS3)$species %>% as_tibble(rownames = "Label")
biplot.df2$Score <- "Species"
biplot.df <- rbind(biplot.df1, biplot.df2) %>% filter(!is.na(NMDS1))


#filter Bug segments to only include the largest effect
biplot.df3 <- scores(NMDS3)$species %>% as_tibble(rownames = "Label") %>% filter(abs(NMDS1) > 1 | abs(NMDS2) > 1)

biplot.df3$Score <- "Species"
biplot.df4 <- rbind(biplot.df1, biplot.df3) 

ggbiplot <- scores(NMDS3)$sites %>% as_tibble(rownames = "Sample") %>%
  left_join(OneBug.wide.Van.Cecum.md, by = "Sample" ) %>%
  ggplot(aes(NMDS1, NMDS2, colour = as.character(Day))) +
  geom_point() + #biplot.df will give all the segments
  geom_segment(data = filter(biplot.df4, Score == "Species"), 
               aes(x = 0, xend = NMDS1, y = 0, yend = NMDS2), inherit.aes = FALSE, size = 0.2) +
  xlim(c(-9,9)) +
  ggtitle(paste0(BUGID," neighbourhoods in Vancomycin, Cecum"))


biplot.df4$Label[106:112] <- c(
   "2: C. scindens",
   "4: O. valericigenes 2"  ,                                                               
"9: K. alysoides"     ,                 
"121: Duncaniella dubosii 4"  ,                                                                       
"257: Marvinbryantia formatexigens 2" ,                                                               
"7: B. crossotus"    ,                                      
"22: E. coli"          
)


ggbiplot + geom_text(data = filter(biplot.df4, Score == "Species"), aes(x = NMDS1, y = NMDS2, label = Label), inherit.aes = FALSE, size = 4) + theme(text = element_text(size = 18))
```
# After revisions biplot by treatment
```{r}
# Filter
OneBug.wide.Van.Cecum <- OneBug %>% filter(Tissue == "CECUM", Day == 35) %>% 
  dplyr::select(ASV_Cluster_Scientific_Name, Sample, Affinity_Score) %>% pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score)

# Change NA to 0 (NAs come from not existing in the affinity matrix)
OneBug.wide.Van.Cecum[is.na(OneBug.wide.Van.Cecum)] <- 0
OneBug.wide.Van.Cecum <- OneBug.wide.Van.Cecum %>% column_to_rownames("Sample")

#Make NMDS
NMDS3 <- metaMDS(OneBug.wide.Van.Cecum, k = 2, trymax = 100, trace = F, autotransform = FALSE, distance="bray")

# get sample metadata 
OneBug.wide.Van.Cecum.md <- OneBug %>% filter(Tissue == "CECUM", Treatment == "Vancomycin") %>% 
  dplyr::select(ASV_Cluster_Scientific_Name, Sample, Affinity_Score, Treatment, Tissue, Day) %>% pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score) %>% .[1:4]

biplot.df1 <- scores(NMDS3)$sites %>% as_tibble(rownames = "Sample") %>%
  left_join(OneBug.wide.Van.Cecum.md, by = "Sample" ) %>% dplyr::select(Sample, NMDS1, NMDS2)

biplot.df1$Score <- "Site"
colnames(biplot.df1)[1] <- "Label"

biplot.df2 <- scores(NMDS3)$species %>% as_tibble(rownames = "Label")
biplot.df2$Score <- "Species"
biplot.df <- rbind(biplot.df1, biplot.df2) %>% filter(!is.na(NMDS1))


#filter Bug segments to only include the largest effect
biplot.df3 <- scores(NMDS3)$species %>% as_tibble(rownames = "Label") %>% filter(abs(NMDS1) > 1 | abs(NMDS2) > 1)

biplot.df3$Score <- "Species"
biplot.df4 <- rbind(biplot.df1, biplot.df3) 

ggbiplot <- scores(NMDS3)$sites %>% as_tibble(rownames = "Sample") %>%
  left_join(OneBug.wide.Van.Cecum.md, by = "Sample" ) %>%
  ggplot(aes(NMDS1, NMDS2, colour = as.character(Day))) +
  geom_point() + #biplot.df will give all the segments
  geom_segment(data = filter(biplot.df4, Score == "Species"), 
               aes(x = 0, xend = NMDS1, y = 0, yend = NMDS2), inherit.aes = FALSE, size = 0.2) +
  xlim(c(-9,9)) +
  ggtitle(paste0(BUGID," neighbourhoods in Vancomycin, Cecum"))


biplot.df4$Label[106:112] <- c(
   "2: C. scindens",
   "4: O. valericigenes 2"  ,                                                               
"9: K. alysoides"     ,                 
"121: Duncaniella dubosii 4"  ,                                                                       
"257: Marvinbryantia formatexigens 2" ,                                                               
"7: B. crossotus"    ,                                      
"22: E. coli"          
)


ggbiplot + geom_text(data = filter(biplot.df4, Score == "Species"), aes(x = NMDS1, y = NMDS2, label = Label), inherit.aes = FALSE, size = 4) + theme(text = element_text(size = 18))
```

# Figure 5c Coefficient plots
```{r}
# Coefficients plots
OneBug.wide.md <- OneBug %>% dplyr::select(Affinity_Score, ASV_Cluster_Scientific_Name, Sample, Tissue, Day, Treatment) %>%
  pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score)
OneBug.wide <- OneBug.wide %>% column_to_rownames("Sample")
adonis.143 <- adonis(select_if(OneBug.wide, is.numeric) ~ Tissue*Treatment*Day, data = OneBug.wide.md, parallel = 2)
coef <- coefficients(adonis.143)["Tissue1",]
top.coef <- coef[rev(order(abs(coef)))[1:10]]
# shorten names for plot
top.coef2 <- top.coef %>% as.data.frame() %>% rownames_to_column("Taxa")
top.coef2
top.coef2$Taxa <- c(
  "O. valericigenes 2",	
"R. peoriensis"	,
"L. phytofermentans",
"C. colinum"	,
"C. scindens",
"O. valericigenes 1",	
"D. dubosii 4"	,
"B. pectinophilus",
"P. capillosus"	,
"A. rubiinfantis"
)

colnames(top.coef2)[2] <- "Coefficient"
top.coef2 %>% ggplot(aes(x = reorder(Taxa, Coefficient), y =Coefficient)) + geom_bar(stat = "identity") + coord_flip() + theme(text = element_text(size = 18))
#ggsave("../Figures/Spatial/Figure5c.pdf", height = 5)
```

# Functions for ST1
```{r}
get.matrix <- function(df, BUG, Tissue, Abx) {
  # The ASV Cluster ID
  BUGID <- BUG 
  # The tissue group you want to compare
  Tis <- Tissue
  # The treatment group you want to compare
  Tx <- Abx
   
  # Filter  
  OneBug.wide <- df %>% filter(Center_Bug == BUGID) %>% filter(Tissue == Tis, Treatment == Tx) %>% filter(Day == 35 | Day == -8) %>%
    select(ASV_Cluster_Scientific_Name, Sample, Affinity_Score) %>%
    pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score, values_fill = 0) %>% column_to_rownames("Sample")
   #remove empty dfs
}

get.md <- function(df, BUG, Tissue, Abx) { # get sample metadata 
  # The ASV Cluster ID
  BUGID <- BUG 
  # The tissue group you want to compare
  Tis <- Tissue
  # The treatment group you want to compare
  Tx <- Abx
  OneBug.wide.md <- df %>% filter(Center_Bug == BUGID) %>% filter(Tissue == Tis, Treatment == Tx) %>% filter(Day == 35 | Day == -8) %>%
     select(ASV_Cluster_Scientific_Name, Sample, Affinity_Score, Treatment, Tissue, Day, Center_Bug) %>%
     pivot_wider(names_from = ASV_Cluster_Scientific_Name, values_from = Affinity_Score) 
}

```

# Suplemental Table 1
```{r}
# mapply with 3 lists, one for BUGID, one for tissue, and one for antibiotics
Bugs <- Affinity.long$Center_Bug %>% unique
Bug.list <- lapply(Bugs, rep, 6) %>% unlist()
Tissue.list <- c("CECUM", "COLON") %>% rep(length(Bugs)*3)
Abx.list <- rep(c(rep("Ampicillin", 2), rep("Vancomycin", 2), rep("H2O", 2)), times = length(Bugs))

Affinity.long$Sample <- paste(Affinity.long$Treatment, Affinity.long$Day, Affinity.long$Tissue, 
                                Affinity.long$Mouse, Affinity.long$Section, Affinity.long$FoV, sep = "_") 

ldf <- list(Affinity.long)

mlist <- mapply(get.matrix, ldf, Bug.list, Tissue.list, Abx.list)
#get rid of empty dfs
mlist <- mlist[sapply(mlist, function(x) dim(x)[1]) > 1]

mdlist<- mapply(get.md, ldf, Bug.list, Tissue.list, Abx.list)

#get rid of empty dfs
mdlist <- mdlist[sapply(mdlist, function(x) dim(x)[1]) > 1]

#remove dfs that only have one type of Day, where you can't do a comparison
mdlistnew <- list()
for (i in 1:length(mdlist)) {
  if (length(unique(mdlist[[i]]$Day)) >1) 
    {mdlistnew[[i]] <- mdlist[[i]]}
}
length(mdlistnew)


mlistnew <- list()
for (i in 1:length(mdlist)) {
  if (length(unique(mdlist[[i]]$Day)) >1) 
    {mlistnew[[i]] <- mlist[[i]]}
}
length(mlistnew)
mlistnew <- mlistnew[lengths(mlistnew) != 0]
mdlistnew <- mdlistnew[lengths(mdlistnew) != 0]

datalist = list()  

for(i in 1:length(mlistnew)) {
  #get the matrix and metadata for each center bug
  mdlistnew[[i]] <- select(mdlistnew[[i]], Sample:Center_Bug) 
  # do adonis on each matrix x metadata
  results <- adonis(mlistnew[[i]] ~ Day, mdlistnew[[i]], parallel = 2, na.rm = TRUE) 
  #put the results into a df
  a.df <- results$aov.tab %>% as.data.frame()
  # add a group to know what we're comparing
  a.df$Group <- paste(mdlistnew[[i]]$Treatment, mdlistnew[[i]]$Tissue, sep = "_") %>% unique()
  # add in the center bug
  a.df$CenterBug <- mdlistnew[[i]]$Center_Bug %>% unique()
  datalist[[i]] <- a.df
}

big_data <- do.call(rbind, datalist)

AdonisResults <- big_data %>% filter(!is.na(`Pr(>F)`)) %>% filter(`Pr(>F)` < 0.1) %>% arrange(-R2)

datalist2 <- list()  

for(i in 1:length(mlistnew)) {
  #get the matrix and metadata for each center bug
  mdlistnew[[i]] <- select(mdlistnew[[i]], Sample:Center_Bug) 
  # do adonis on each matrix x metadata
  results <- adonis(mlistnew[[i]] ~ Day, mdlistnew[[i]], parallel = 2, na.rm = TRUE) 
  #put the coefficients into a df
  coef <- coefficients(results)["Day",] %>% as.data.frame()
  names(coef) <- "value"
  top.coef <- coef %>% drop_na() %>% arrange(-abs(value)) %>% rownames_to_column("Neighbour_Bug")
  # add a group to know what we're comparing
  top.coef$Group <- paste(mdlistnew[[i]]$Treatment, mdlistnew[[i]]$Tissue, sep = "_") %>% unique()
  # add in the center bug
  top.coef$CenterBug <- mdlistnew[[i]]$Center_Bug %>% unique()
  datalist2[[i]] <- top.coef[1,]
}

big_data2 <- do.call(rbind, datalist2)


#join together
FullPermanova <- inner_join(AdonisResults, big_data2, by = c("Group", "CenterBug"))
FullPermanova <- FullPermanova %>% select(`Pr(>F)`, Group, CenterBug, Neighbour_Bug, value, R2)
#add in name of CenterBug
FullPermanova$CenterBug <- as.character(FullPermanova$CenterBug)
FullPermanova <- FullPermanova %>% left_join(select(ASV, ASV_Cluster_ID, ASV_Cluster_Scientific_Name) , by = c("CenterBug" = "ASV_Cluster_ID"))
colnames(FullPermanova)[7] <- "CenterBugName"
colnames(FullPermanova)[1] <- "pValue"
colnames(FullPermanova)[5] <- "coefficient"

FullPermanova <- separate(FullPermanova, Group, into = c("Treatment", "Tissue"), sep = "\\_")
FullPermanova %>% filter(CenterBug == 30)
#write.csv(PermanovaResults.csv")
#write.csv(Revisions/SupplementalTable1.csv")
```

# Source in the preprocessed spatial data for the image level analysis
```{r}
source("Functions.R")
suppressWarnings(suppressMessages(source("Image_Counts_by_FoV.R"))) # outputs Counts.summary and raw.data.wide and md.images
raw.data.wide
Counts.summary
```

# Make Counts.wide
```{r}
Counts.df <- raw.data.wide %>% group_by(ASV_Cluster_ID, Mouse, Tissue, Section, FoV) %>% summarize(Count = n()) %>% group_by(Mouse, Tissue, Section, FoV) %>%  mutate(Total = sum(Count))

#join it with metadata 
Counts.df <- left_join(Counts.df, md.images, by = "Mouse")
Counts.df$ASV_Cluster_ID <- as.character(Counts.df$ASV_Cluster_ID)

ASV <- read.csv("../data/asv_lineage_abundance.csv")
ASV$ASV_Cluster_ID <- as.character(ASV$ASV_Cluster_ID)
Counts.df <- left_join(Counts.df, dplyr::select(ASV, 1:2), by = "ASV_Cluster_ID" )
Counts.df <- Counts.df %>% mutate_at("ASV_Cluster_Scientific_Name", ~replace_na(.,"Bacteria"))

# Species counts per tx
Counts.df <- Counts.df %>% group_by(Mouse, Tissue, Section, FoV) %>% mutate(SpeciesCount = n_distinct(ASV_Cluster_ID))

# Fix factor levels and change H2O to water
Counts.df$Treatment <- gsub("H2O", "Water", Counts.df$Treatment) #changes H20 to water with pattern matching
Counts.df$Treatment <- as.factor(Counts.df$Treatment) # make them as factors
Counts.df$Treatment <- factor(Counts.df$Treatment, levels=c('Water', 'Ampicillin', 'Vancomycin')) # change their order

Counts.df$Sample <- paste(Counts.df$Treatment, Counts.df$Day, Counts.df$Tissue, Counts.df$Mouse, Counts.df$Section, Counts.df$FoV, sep = "_") 

# Make Counts.wide
Counts.wide <- Counts.df %>% dplyr::select(Sample, ASV_Cluster_ID, Count) %>% pivot_wider(names_from = ASV_Cluster_ID, values_from = Count) %>% .[,5:69] %>% column_to_rownames("Sample")

Counts.wide <- replace(Counts.wide,is.na(Counts.wide),0)
```

# Get BC
```{r}
All.BC <- vegdist(Counts.wide, "bray")
hist(All.BC, xlim = range(0.0,1.0))

All.BC.mat <- as.matrix(All.BC) 
All.BC.mat[lower.tri(All.BC.mat)] <- NA
All.BC.df <- All.BC.mat %>% as.data.frame() %>% rownames_to_column("Var1")  %>% pivot_longer(-Var1, names_to = "Var2", values_to = "BC") 

# add in metadata
All.BC.df.md <- left_join(All.BC.df, 
                          dplyr::select(Counts.df, 
                                        c(Mouse, Tissue, Section, FoV, Treatment, Day, Sample)), 
                          by = c("Var1" = "Sample")) %>%
  filter(Var1 != Var2)  %>% # removes self comparisons
  distinct()

All.BC.df.md <- left_join(All.BC.df.md,
                          dplyr::select(Counts.df, c(Mouse, Tissue, Section, FoV, Treatment, Day, Sample)),
                          by = c("Var2" = "Sample")) %>%
  filter(Var1 != Var2)  %>%
  distinct() # removes self comparisons

All.BC.df.md %>% filter(Tissue.x == Tissue.y) %>% filter(Treatment.x == "Water") %>% filter(!is.na(BC)) %>% filter(Day.x == 35 & Day.y == 35) %>% group_by(Treatment.x, Treatment.y, Day.x, Day.y, Tissue.x, Tissue.y) %>% count
```

# Correlation between abundance at baseline and and how well the community recovers
```{r}
long.0 <- Counts.wide %>% rownames_to_column("Sample") %>% pivot_longer(-Sample, names_to = "BugID", values_to = "Count")
buglist <- long.0$BugID %>% unique

# Within a tissue type and treatment, get the average diversity difference 
ks <- All.BC.df.md %>% filter(Tissue.x == Tissue.y) %>% filter(Treatment.x == Treatment.y) %>% filter(Day.x == -8, Day.y == 35)



# For every bug, correlate it's abundance in every sample to that sample's 'recovery score' which is just 1-BC Day 35 to Day -8
resultlist <- list()
for (bug in 1:length(buglist)) {
  long.2 <- long.0 %>% filter(BugID == buglist[[bug]]) %>%
    separate(Sample, c("Treatment", "Day", "Tissue", "Mouse", "Section", "FoV"), remove = FALSE)
  baseline <- ks %>% left_join(long.2, by = c("Var1" = "Sample") ) %>% mutate(Recovery = 1 - BC)
  result <- baseline %>% group_by(Treatment, Tissue) %>% cor_test(Recovery, Count)
  result$Bug <- buglist[[bug]]
  resultlist[[bug]] <- result
}

Corr.results <- do.call(rbind, resultlist)
Corr.results$Bug <- as.numeric(Corr.results$Bug)

# THIS GIVE HOW MANY UNIQUE BUGS SHOW UP FOR A CENTER BUG PER SAMPLE
SpeciesCount <- Affinity.long %>% filter(Day == -8, Affinity_Score != 0) %>% group_by(Center_Bug, Tissue, Treatment, Mouse, Section, FoV) %>% summarize(Uniqeue = n())

# Now add the neighbourhood richness for each bug
SpeciesCount2 <- SpeciesCount %>% group_by(Tissue, Center_Bug) %>% summarize(neighRichness = mean(Uniqeue))
Corr2.results <- Corr.results %>% left_join(SpeciesCount2, join_by(Bug == Center_Bug, Tissue), keep = TRUE) %>% distinct %>% filter(p < 0.05)

MT_correlation <- Corr2.results %>% group_by(Tissue.x, Treatment) %>% cor_test(cor, neighRichness)
```

# Figure 6 heatmaps
```{r}
#Corr2.results %>% select(Treatment, Tissue.x, Bug, neighRichness, cor) %>% arrange(Bug, neighRichness)

Corr2.results <- Corr2.results %>% select(Treatment, Tissue.x, Bug, neighRichness, cor)
# treatment order
col_order <- c( "Vancomycin", "Ampicillin", "Water")

# Cecum
test.cecum <- Corr2.results %>% filter(Tissue.x == "CECUM") %>% arrange(neighRichness) %>%
  select(Treatment, cor, Bug) %>% filter(!is.na(cor)) %>% distinct() %>% filter(Bug != -1)

test.cecum <- pivot_wider(test.cecum, names_from = Treatment, values_from = cor) %>% filter(!is.na(cor)) %>% column_to_rownames("Bug") %>%  as.matrix
test.cecum <- test.cecum[, col_order]

# colon
test.colon <- Corr2.results %>% filter(Tissue.x == "COLON") %>% arrange(neighRichness) %>% select(Treatment, cor, Bug) %>% filter(!is.na(cor)) %>% distinct() %>% filter(Bug != -1)

test.colon <- pivot_wider(test.colon, names_from = Treatment, values_from = cor) %>% filter(!is.na(cor)) %>% column_to_rownames("Bug") %>%  as.matrix
test.colon <- test.colon[, col_order]

breaksList = seq(-0.6, 0.6, by = 0.05)

#pheatmap(test.colon, cluster_rows = FALSE, cluster_cols = FALSE, main = "COLON", fontsize = 14, height = 12, width = 3, angle_col = 315, breaks =  breaksList , color = colorRampPalette(c("navy", "white", "red"))(length(breaksList)), filename = "../Figures/Colon_MashasCorrelation2.pdf")

#pheatmap(test.cecum, cluster_rows = FALSE, cluster_cols = FALSE, main = "COLON", fontsize = 14, height = 12, width = 3, angle_col = 315, breaks =  breaksList , color = colorRampPalette(c("navy", "white", "red"))(length(breaksList)), filename = "../Figures/Cecum_MashasCorrelation2.pdf" )

```


# Neigborhood richness boxplots
```{r}
abundance.summary <- Counts.df %>%  ungroup() %>% group_by(ASV_Cluster_ID) %>% summarize(ImageAbundance = mean(Count), sd = sd(Count))
colnames(abundance.summary)[1] <- "Center_Bug"
abundance.summary$Center_Bug <- as.numeric(abundance.summary$Center_Bug)


# remove center bugs that are absent in the masha's correlation heatmap
to.remove.cec <- c(104, 145)
to.keep.cec <- setdiff(unique(SpeciesCount$Center_Bug), to.remove.cec)
to.remove.col <- c(36, 104, 21, 204, 133)
to.keep.col <- setdiff(unique(SpeciesCount$Center_Bug), to.remove.col)

# CECUM
left_join(SpeciesCount, abundance.summary, by = "Center_Bug" ) %>% filter(Tissue == "CECUM") %>% filter(Center_Bug %in% to.keep.cec) %>%
  ggplot(aes(x = reorder(as.character(Center_Bug), Uniqeue, FUN = mean), y = Uniqeue)) + 
  geom_boxplot(aes( fill = log(ImageAbundance))) +
  xlab("Center_Bacteria") +
  ylab("SpeciesRichness") +
  ggtitle("CECUM: Baseline neighbourhood diversity") +
  theme_bw() +
  theme(text = element_text(size = 16), legend.position = "none")   +
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
#ggsave("../Figures/Spatial/Neighbourhood_SpeciesRichness_fixedAbundance_CECUM2.pdf", height = 4, width = 14)

# COLON
left_join(SpeciesCount, abundance.summary, by = "Center_Bug" ) %>% filter(Tissue == "COLON") %>% filter(Center_Bug %in% to.keep.col) %>%
  ggplot(aes(x = reorder(as.character(Center_Bug), Uniqeue, FUN = mean), y = Uniqeue)) + 
  geom_boxplot(aes( fill = log(ImageAbundance))) +
  xlab("Center_Bacteria") +
  ylab("SpeciesRichness") +
  ggtitle("COLON: Baseline neighbourhood diversity") +
  theme_bw() +
  theme(text = element_text(size = 16), legend.position = "none")   +
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
#ggsave("../Figures/Spatial/Neighbourhood_SpeciesRichness_fixedAbundance_COLON2.pdf", height = 4, width = 14)

Richness <- left_join(SpeciesCount, abundance.summary, by = "Center_Bug" ) %>% filter(Tissue == "CECUM") %>% group_by(Center_Bug) %>% summarize(NeighbRich = median(Uniqeue)) 

n <- 25
bugs.top25.rich <- Richness[Richness$NeighbRich > quantile(Richness$NeighbRich,prob=1-n/100),]

Abundance <- left_join(SpeciesCount, abundance.summary, by = "Center_Bug" ) %>% ungroup() %>% select(Center_Bug, ImageAbundance) %>% distinct()

n <- 20
bugs.bottom25.abundance <- Abundance[Abundance$ImageAbundance < quantile(Abundance$ImageAbundance,prob=1-n/100),]

# look for overlap of high richness low abundance
intersect(bugs.top25.rich$Center_Bug, bugs.bottom25.abundance$Center_Bug)

# Bug 198 is in the top 25% for neihgborhood rihcness, but bottom 75% for abundnace
# Bugs 2, 13, 46, 121, 147, 198, 257 are in the top 25% fo rneihgborhood richness, but bottom 90% for abundance
# Bugs 2,  46,  198 are in the top 25% for neihgborhood richness, but bottom 80% for abundance

# look for overlap with high correlation
highcor <- read.csv("../Results/cecum_mashascorrelation_high.csv")
highcor
highcor$Bug
intersect(intersect(bugs.top25.rich$Center_Bug, bugs.bottom25.abundance$Center_Bug), importance.25.Bug)

```
# After revisions redoing Fig 6 heatmaps to compare day 35 to water rather than to baseline
```{r}
# Correlation between abundance at baseline and and how well the community recovers

long.0 <- Counts.wide %>% rownames_to_column("Sample") %>% pivot_longer(-Sample, names_to = "BugID", values_to = "Count")
buglist <- long.0$BugID %>% unique

# Within a tissue type, get the average diversity difference between treatment and water at day 35
ks <- All.BC.df.md %>% filter(Tissue.x == Tissue.y) %>% filter(Treatment.x == "Water") %>% filter(!is.na(BC)) %>% filter(Day.x == 35 & Day.y == 35)



# For every bug, correlate it's abundance in every sample to that sample's 'recovery score' which is just 1-BC Abx to water
resultlist <- list()
for (bug in 1:length(buglist)) {
  long.2 <- long.0 %>% filter(BugID == buglist[[bug]]) %>%
    separate(Sample, c("Treatment", "Day", "Tissue", "Mouse", "Section", "FoV"), remove = FALSE)
  baseline <- ks %>% left_join(long.2, by = c("Var1" = "Sample") ) %>% mutate(Recovery = 1 - BC)
  result <- baseline %>% group_by(Treatment.y, Tissue) %>% cor_test(Recovery, Count)
  result$Bug <- buglist[[bug]]
  resultlist[[bug]] <- result
}

Corr.results <- do.call(rbind, resultlist)
Corr.results$Bug <- as.numeric(Corr.results$Bug)

# THIS GIVE HOW MANY UNIQUE BUGS SHOW UP FOR A CENTER BUG PER SAMPLE
SpeciesCount <- Affinity.long %>% filter(Treatment == "H2O", Affinity_Score != 0) %>% group_by(Center_Bug, Tissue, Treatment, Mouse, Section, FoV) %>% summarize(Uniqeue = n())

# Now add the neighbourhood richness for each bug
SpeciesCount2 <- SpeciesCount %>% group_by(Tissue, Center_Bug) %>% summarize(neighRichness = mean(Uniqeue))
Corr2.results <- Corr.results %>% left_join(SpeciesCount2, join_by(Bug == Center_Bug, Tissue), keep = TRUE) %>% distinct %>% filter(p < 0.05)

MT_correlation <- Corr2.results %>% group_by(Tissue.x, Treatment.y) %>% cor_test(cor, neighRichness)
```

# Figure 6 heatmaps
```{r}
#Corr2.results %>% select(Treatment, Tissue.x, Bug, neighRichness, cor) %>% arrange(Bug, neighRichness)

Corr2.results <- Corr2.results %>% dplyr::select(Treatment.y, Tissue.x, Bug, neighRichness, cor)
# treatment order
col_order <- c("Ampicillin",  "Vancomycin")

# Cecum
test.cecum <- Corr2.results %>% filter(Tissue.x == "CECUM") %>% arrange(neighRichness) %>%
  dplyr::select(Treatment.y, cor, Bug) %>% filter(!is.na(cor)) %>% distinct() %>% filter(Bug != -1)

test.cecum <- pivot_wider(test.cecum, names_from = Treatment.y, values_from = cor) %>% filter(!is.na(cor)) %>% column_to_rownames("Bug") %>% dplyr::select(-Water) %>%as.matrix
test.cecum <- test.cecum[, col_order]

# colon
test.colon <- Corr2.results %>% filter(Tissue.x == "COLON") %>% arrange(neighRichness) %>%
  dplyr::select(Treatment.y, cor, Bug) %>% filter(!is.na(cor)) %>% distinct() %>% filter(Bug != -1)

test.colon <- pivot_wider(test.colon, names_from = Treatment.y, values_from = cor) %>% filter(!is.na(cor)) %>% column_to_rownames("Bug") %>% dplyr::select(-Water) %>% as.matrix
test.colon <- test.colon[, col_order]

breaksList = seq(-0.6, 0.6, by = 0.05)

pheatmap(test.colon, cluster_rows = FALSE, cluster_cols = FALSE, main = "COLON", fontsize = 14, height = 12, width = 3, angle_col = 315, breaks =  breaksList , color = colorRampPalette(c("navy", "white", "red"))(length(breaksList)))

pheatmap(test.cecum, cluster_rows = FALSE, cluster_cols = FALSE, main = "CECUM", fontsize = 14, height = 12, width = 3, angle_col = 315, breaks =  breaksList , color = colorRampPalette(c("navy", "white", "red"))(length(breaksList)))

```
```

