---
title: "Image diversity analysis"
output: html_notebook
---

# Mariia Taguer
# Mar 2 2023
# Kanvas Spatial Analysis

# Load in libraries
```{r}
library(tidyverse)
library(vegan)
theme_set(theme_bw(base_size = 16))
library(RColorBrewer)
library(ggpubr)
library(rstatix)
library(umap)
```


# Load image count data that was generated with "Image_Diversity_Prep.R"
```{r}
# set Analysis as your working directory
Counts.df <- read.csv("../data/Counts_df.csv") %>% select(-1) # removes rownumbers
# turn treatment into factor for ordering
Counts.df$Treatment <- factor(Counts.df$Treatment, levels=c('Water', 'Ampicillin', 'Vancomycin')) # change their order

# Set colour palette
colours <- c("#335780", "#96BBE4", "#D5490C",
          "#F1BA69",  "#03663F", "#71D68E")
```


# FIGURE 2BC Alpha Diversity 
```{r}
# Stats
SpeciesCounts.stats <- Counts.df %>% select(Tissue, Mouse, Section, FoV, SpeciesCount, Treatment, Day) %>% distinct() %>% 
  group_by(Tissue, Treatment) %>% 
   rstatix::pairwise_wilcox_test(SpeciesCount ~ Day, ref.group = "-8") %>% add_xy_position(x = "Day")


Counts.df %>% select(Tissue, Mouse, Section, FoV, SpeciesCount, Treatment, Day) %>% distinct() %>%
  ggplot(aes(x = as.character(Day), y = SpeciesCount, colour = interaction(Tissue,Treatment, sep = ":"))) + 
  geom_violin(scale = "width", draw_quantiles = 0.5) + geom_jitter(width = 0.2, alpha = 0.2)  + 
  facet_grid(Tissue ~ Treatment) +
  ggtitle("Species Abundance") +
  xlab("Day") +
  theme(text = element_text(size = 20)) +
  stat_pvalue_manual(SpeciesCounts.stats, hide.ns = TRUE, size = 6, bracket.nudge.y = 20) +
    theme(text = element_text(size = 20))  +
  ylim(0,90) +
  scale_colour_manual(values=colours) +
  labs(color = "Tissue and Treatment")  

#ggsave("../Figures/SpeciesCountViolin.pdf", height = 5, width = 9)


# SHANNON
# matrix samples are rows species are columns
Counts.df$Sample <- paste(Counts.df$Treatment, Counts.df$Day, Counts.df$Tissue, Counts.df$Mouse, Counts.df$Section, Counts.df$FoV, sep = "_") 

Counts.wide <- Counts.df %>% select(Sample, ASV_Cluster_ID, Count) %>%
  pivot_wider(names_from = ASV_Cluster_ID, values_from = Count) %>% .[,5:69] %>%
  column_to_rownames("Sample")

# replace NA with 0
Counts.wide[is.na(Counts.wide)] <- 0
Shannon <- diversity(Counts.wide) 
Shannon <- Shannon %>% as.data.frame()
colnames(Shannon) <- "Shannon"
Shannon <- Shannon %>% rownames_to_column("Sample")

Alpha.Div <- Counts.df %>% pivot_wider(names_from = ASV_Cluster_ID, values_from = Count) %>%
  select(Tissue, Treatment, Day, Sample) %>% right_join(Shannon, by = "Sample")

# do the stats
Shannon.stats <- Alpha.Div %>% select(Tissue, Mouse, Section, FoV, Shannon, Treatment, Day) %>%
  distinct() %>% group_by(Tissue, Treatment) %>% 
   rstatix::pairwise_wilcox_test(Shannon ~ Day, ref.group = "-8") %>% add_xy_position(x = "Day")


#Compare between tissues
Shannon.stats2 <- Alpha.Div %>% select(Tissue, Mouse, Section, FoV, Shannon, Treatment, Day) %>% distinct() %>% 
  group_by(Day, Treatment) %>% 
   rstatix::pairwise_wilcox_test(Shannon ~ Tissue) %>% add_xy_position(x = "Day")


#Compare to baseline
Shannon.stats <- Alpha.Div %>% ungroup() %>% select(Mouse, Tissue, Section, FoV, Shannon, Treatment, Day) %>% distinct() %>% 
  group_by(Tissue, Treatment) %>% rstatix::wilcox_test(Shannon ~ Day, ref.group = "-8") %>% add_xy_position(x = "Day")

# FIGURE 2C
Alpha.Div %>% ungroup() %>% distinct() %>% 
  ggplot(aes(x = as.character(Day), y = Shannon, colour = interaction(Tissue,Treatment, sep = ":"))) + 
  geom_violin(scale = "width", draw_quantiles = 0.5) + geom_jitter(width = 0.2, alpha = 0.3)  + 
  facet_grid(Tissue~Treatment) +
  ggtitle("Shannon") +
  xlab("Day") +
  theme(text = element_text(size = 20)) +
  stat_pvalue_manual(Shannon.stats, hide.ns = TRUE, size = 6) +
    theme(text = element_text(size = 20))  +
  ylim(c(0,3.5)) +
  scale_colour_manual(values=colours) +
  labs(color = "Tissue and Treatment") 
#ggsave("../Figures/ShannonImagingTissuesViolin.pdf", height = 5, width = 9)
```

# Figure 2D
```{r}
BaselineShannon <- Alpha.Div %>% distinct() %>% group_by(Tissue, Treatment, Day) %>% mutate(BaselineShannon = mean(Shannon)) %>% filter(Day == -8) %>% select(4:5, 9) %>% distinct()

Delta.Shannon <- Alpha.Div %>% ungroup() %>% left_join(BaselineShannon, by = c("Tissue", "Treatment")) %>% mutate(Delta = Shannon - BaselineShannon)

# ShannonDelta Stats
ShannonDelta.stats <- Delta.Shannon %>% select(Sample, Tissue, Treatment, Day.x, Delta) %>% distinct() %>% filter(Day.x != -8) %>% group_by(Treatment, Day.x) %>%  rstatix::pairwise_wilcox_test(Delta ~ Tissue) %>% add_xy_position(x = "Day.x")

# FIGURE 1D
Delta.Shannon %>% select(Sample, Tissue, Treatment, Day.x, Delta) %>% distinct() %>% filter(Day.x != -8) %>%
  ggplot(aes(x = as.character(Day.x), y = Delta, colour = interaction(Tissue,Treatment, sep = ":"))) +
  geom_violin(scale = "width", draw_quantiles = 0.5) + 
  geom_point(position=position_jitterdodge(), alpha = 0.3)  +
  facet_grid(.~Treatment) +
  stat_pvalue_manual(ShannonDelta.stats, hide.ns = TRUE, size = 6) +
    theme(text = element_text(size = 20))  +
  xlab("Day") +
  ylab("Delta Shannon") +
  scale_colour_manual(values=colours) 
#ggsave("../Figures/ShannonDeltaImagingviolin.pdf", height = 3.8, width = 11.5)
```

# Figure 2A
```{r}
Counts.stats <- Counts.df %>% ungroup() %>% select(Mouse, Tissue, Section, FoV, Total, Treatment, Day) %>% distinct() %>% 
  group_by(Tissue, Treatment) %>% rstatix::wilcox_test(Total ~ Day, ref.group = "-8") %>% add_xy_position(x = "Day")

# FIGURE 2A  
Counts.df %>% ungroup() %>% select(Mouse, Tissue, Section, FoV, Total, Treatment, Day) %>% distinct() %>% 
  ggplot(aes(x = as.character(Day), y = Total, colour = interaction(Tissue,Treatment, sep = ":"))) +
  geom_violin(scale = "width", draw_quantiles = 0.5) + 
  geom_jitter(width = 0.2, alpha = 0.3)  + 
  facet_grid(Tissue~Treatment) +
  stat_pvalue_manual(Counts.stats, hide.ns = TRUE, size = 6, y.position = 4.4) +
    theme(text = element_text(size = 20))  +
  scale_y_log10(labels = scales::label_log(), limits = c(1, 50000)) +  
  ylab("log HiPR-FISH counts per FoV") + 
  xlab("Day") +
  scale_colour_manual(values=colours) 
#ggsave("../Figures/Spatial/CountsperFOV.pdf", height = 4.5, width = 11)
```

# Stats for 2A
```{r}
HiprFISHcounts <- Counts.df %>% ungroup() %>% select(Mouse, Tissue, Section, FoV, Total, Treatment, Day) %>% distinct() %>% group_by(Treatment, Tissue, Day) %>% summarize(median = median(Total), sd = sd(Total))

write_csv(HiprFISHcounts, "../Results/Table1_HiprFISH_counts.csv")
```

# FIGURE 3a
```{r}
Shannon <- diversity(Counts.wide) 
Shannon <- Shannon %>% as.data.frame()
colnames(Shannon) <- "Shannon"
Shannon <- Shannon %>% rownames_to_column("Sample")

Alpha.Div <- Counts.df %>% pivot_wider(names_from = ASV_Cluster_ID, values_from = Count) %>% select(Tissue, Treatment, Day, Sample) %>% right_join(Shannon, by = "Sample")

# Set colour palette
colours_tissue <- c("#bc85ef", "#E8C351")

# make tissue as factor
Alpha.Div$Tissue <- as.factor(Alpha.Div$Tissue)

#significantly different from normal distribution
Alpha.Div %>% dplyr::filter(Day == -8) %>%  ungroup() %>%  sample_n(1000) %>% rstatix::shapiro_test(Shannon)

#plot
with_water <- Alpha.Div %>% dplyr::filter(Day == -8 | Treatment == "Water") %>% distinct()
with_water %>% ggplot(aes(x = Tissue, y = Shannon)) + geom_boxplot()
with_water2 <- with_water %>% group_by(Tissue) %>% dplyr::summarize(average = mean(Shannon), sd = sd(Shannon))
wilcox.test(average ~ Tissue, data = with_water2, paired = TRUE)

without_water <- Alpha.Div %>% dplyr::filter(Day == -8) %>% distinct()
without_water %>% ggplot(aes(x = Tissue, y = Shannon, colour = Tissue)) + 
  geom_boxplot() +
  ylim(c(0,3)) +
  ggtitle("Baseline") +
  scale_colour_manual(values=colours_tissue)  +
    theme(text = element_text(size = 20)) 
#ggsave("../Figures/Spatial/Baseline_Shannon.pdf", width = 5, height = 3.5)

without_water2 <- without_water %>% group_by(Tissue, Mouse) %>% summarize(average = mean(Shannon), sd = sd(Shannon))
wo_water_stats <- wilcox.test(average ~ Tissue, data = without_water2, paired = TRUE)

#difference in shannon index between tissues
without_water %>% group_by(Tissue) %>% summarize(mean(Shannon))
2.115043 / 1.885505
```

#Figure 2a line 41
```{r}
Counts.df %>% filter(Treatment != "Water") %>% ungroup() %>% select(Mouse, Tissue, Section, FoV, Total, Treatment, Day) %>% distinct() %>% group_by(Tissue, Treatment, Day) %>% summarize(mean(Total), sd(Total))
```


# Beta Diversity: Figure 2E
```{r}
#make observation (sample) by variable df
Counts.df$Sample <- paste(Counts.df$Treatment, Counts.df$Day, Counts.df$Tissue, Counts.df$Mouse, Counts.df$Section, Counts.df$FoV, sep = "_") 
Counts.wide <- Counts.df %>% select(Sample, ASV_Cluster_ID, Count) %>% 
  pivot_wider(Sample, names_from = ASV_Cluster_ID, values_from = Count) 
#turn sample to rowname
Counts.wide <- Counts.wide %>% column_to_rownames("Sample")
Counts.wide <- replace(Counts.wide,is.na(Counts.wide),0)
All.BC <- vegdist(Counts.wide, "bray")

All.BC.mat <- as.matrix(All.BC) 
All.BC.mat[lower.tri(All.BC.mat)] <- NA
All.BC.df <- All.BC.mat %>% as.data.frame() %>% rownames_to_column("Var1")  %>% pivot_longer(-Var1, names_to = "Var2", values_to = "BC") 

# add in metadata
All.BC.df.md <- left_join(All.BC.df, select(Counts.df, c(Mouse, Tissue, Section, FoV, Treatment, Day, Sample)), 
                          by = c("Var1" = "Sample")) %>%
  filter(Var1 != Var2)  %>% # removes self comparisons
  distinct()

All.BC.df.md <- left_join(All.BC.df.md, select(Counts.df, c(Mouse, Tissue, Section, FoV, Treatment, Day, Sample)), 
                          by = c("Var2" = "Sample")) %>%
  filter(Var1 != Var2)  %>% # removes self comparisons
  distinct()

#do the stats
BC.counts.Wilcox <- All.BC.df.md %>% filter(Day.x == -8) %>% filter(Tissue.x == Tissue.y) %>%
  filter(Treatment.x == Treatment.y) %>% group_by(Treatment.x, Tissue.x) %>%
  filter(!is.na(BC))  %>% rstatix::pairwise_wilcox_test(BC ~ Day.y, ref.group = "-8")

BC.counts.Wilcox <- BC.counts.Wilcox %>% add_xy_position(x = "Day.y")
# Boxplot comparing to baseline and only compare within treatments and within tissues

# FIGURE 2E
All.BC.df.md %>% filter(Day.x == -8) %>% filter(Tissue.x == Tissue.y) %>% filter(Treatment.x == Treatment.y) %>% distinct() %>% 
ggplot(aes(x= as.character(Day.y), y=BC, colour = interaction(Tissue.x, Treatment.x))) +
  geom_violin(scale = "width", draw_quantiles = 0.5) + 
  geom_point(position=position_jitterdodge(2), alpha = 0.05)  +  
  ylab("Bray-Curtis dissimilarity") +
  facet_grid(Tissue.x ~ Treatment.x) +
  xlab("Day vs Day -8") +
  theme(text = element_text(size = 20)) +
  ggtitle("Bray curtis on image counts") + 
  stat_pvalue_manual(BC.counts.Wilcox, hide.ns = TRUE, size = 8, step.increase = 0.06, step.group.by = "Tissue.x",
                    bracket.nudge.y = 0.1) +
  ylim(0,1.5) +
  scale_colour_manual(values=colours) 
#ggsave("../Figures/Images_Counts_BC_violin.pdf", height = 5, width = 10.5) 

# Compare between tissue types
#tissue stats
BC.counts.Tissue <- All.BC.df.md %>% filter(Day.x == -8) %>% filter(Tissue.x == Tissue.y) %>% filter(Treatment.x == Treatment.y) %>%  group_by(Treatment.x, Day.y) %>%
filter(!is.na(BC))  %>% rstatix::pairwise_wilcox_test(BC ~ Tissue.x) %>% add_xy_position(x = "Day.y")

All.BC.df.md %>% filter(Day.x == -8) %>% filter(Tissue.x == Tissue.y) %>%
  filter(Treatment.x == Treatment.y) %>% distinct %>%
  ggplot(aes(x= as.character(Day.y), y=BC, colour = interaction(Tissue.x, Treatment.x))) + 
  geom_violin(scale = "width", draw_quantiles = 0.5) + 
  geom_point(position=position_jitterdodge(2), alpha = 0.05)  +  
  ylab("Bray-Curtis dissimilarity") +
  facet_grid(.~ Treatment.x ) +
  xlab("Day vs Day -8") +
  ggtitle("Bray curtis on image counts") +
 stat_pvalue_manual(BC.counts.Tissue, hide.ns = TRUE, size = 6,  bracket.nudge.y = 0.1) +
  theme(text = element_text(size = 20))  +
  ylim(0,1.25)  +
  scale_colour_manual(values=colours) 
#ggsave("../Figures/Images_Delta_BC_violin.pdf", height = 4, width = 10.5)
```

# UMAP FIGURE 3D
```{r}
Counts.df$Sample <- paste(Counts.df$Treatment, Counts.df$Day, Counts.df$Tissue, Counts.df$Mouse, Counts.df$Section, Counts.df$FoV, sep = "_") 
Counts.wide <- Counts.df %>% select(Sample, ASV_Cluster_ID, Count) %>% pivot_wider(names_from = ASV_Cluster_ID, values_from = Count) %>% column_to_rownames("Sample")
# replace NA with 0
Counts.wide[is.na(Counts.wide)] <- 0

umap.counts <- umap(Counts.wide, n_neighbors = 10)

# add the metadata 
umap_df <- umap.counts$layout %>%
  as.data.frame() %>%
  rename(UMAP1="V1",
         UMAP2="V2") %>% 
  rownames_to_column("Sample") %>% 
  separate("Sample", c("Treatment", "Day", "Tissue"), sep = "_")

umap_df$Treatment <- as.factor(umap_df$Treatment)
umap_df$Treatment <- factor(umap_df$Treatment, levels = c("Water", "Ampicillin", "Vancomycin"))

umap_df %>% na.omit() %>%
  ggplot(aes(x = UMAP1, y = UMAP2, color = as.character(Day) ))+
  geom_point(size = 2) +
  facet_grid(Treatment~Tissue) +
  stat_ellipse(type = "t") +
  labs(x = "UMAP1",
       y = "UMAP2",
      title = "Image level") 
#ggsave("../Figures/Spatial/Image_Diversity_counts_UMAP.pdf", width = 8, height = 6)
```

# Figure 3C Permanova
```{r}
counts.wide.log <- Counts.wide + 1
counts.wide.log <- log10(counts.wide.log) 

Cecum.wide.amp <- counts.wide.log %>% rownames_to_column("Sample") %>% filter(grepl("CECUM", Sample )) %>% filter(grepl("Ampicillin", Sample )) %>%
  column_to_rownames("Sample")
Cecum.wide.van <- counts.wide.log %>% rownames_to_column("Sample") %>% filter(grepl("CECUM", Sample )) %>% filter(grepl("Vancomycin", Sample )) %>%
  column_to_rownames("Sample")
Cecum.wide.water <- counts.wide.log %>% rownames_to_column("Sample") %>% filter(grepl("CECUM", Sample )) %>% filter(grepl("Water", Sample )) %>% 
  column_to_rownames("Sample")

Counts.wide.md <- Counts.df %>% select(Sample, ASV_Cluster_ID, Count, Treatment, Day) %>% pivot_wider(names_from = ASV_Cluster_ID, values_from = Count) %>% .[,5:69] %>% column_to_rownames("Sample")

Cecum.wide.amp.md <- Counts.wide.md %>% rownames_to_column("Sample") %>% filter(grepl("CECUM", Sample )) %>% filter(grepl("Ampicillin", Sample )) %>%
  column_to_rownames("Sample")
Cecum.wide.van.md <- Counts.wide.md %>% rownames_to_column("Sample") %>% filter(grepl("CECUM", Sample )) %>% filter(grepl("Vancomycin", Sample )) %>%
  column_to_rownames("Sample")
Cecum.wide.water.md <- Counts.wide.md %>% rownames_to_column("Sample") %>% filter(grepl("CECUM", Sample )) %>% filter(grepl("Water", Sample )) %>% 
  column_to_rownames("Sample")

permanova.cecum.amp <- adonis(Cecum.wide.amp ~ Day, Cecum.wide.amp.md)
permanova.cecum.van <- adonis(Cecum.wide.van ~ Day, Cecum.wide.van.md)
permanova.cecum.water <- adonis(Cecum.wide.water ~ Day, Cecum.wide.water.md)
permanova.cecum.amp$aov.tab
permanova.cecum.van$aov.tab
permanova.cecum.water$aov.tab

# COLON
Colon.wide.amp <- counts.wide.log %>% rownames_to_column("Sample") %>% filter(grepl("COLON", Sample )) %>% filter(grepl("Ampicillin", Sample )) %>%
  column_to_rownames("Sample")
Colon.wide.van <- counts.wide.log %>% rownames_to_column("Sample") %>% filter(grepl("COLON", Sample )) %>% filter(grepl("Vancomycin", Sample )) %>%
  column_to_rownames("Sample")
Colon.wide.water <- counts.wide.log %>% rownames_to_column("Sample") %>% filter(grepl("COLON", Sample )) %>% filter(grepl("Water", Sample )) %>% 
  column_to_rownames("Sample")

Counts.wide.md <- Counts.df %>% select(Sample, ASV_Cluster_ID, Count, Treatment, Day) %>% pivot_wider(names_from = ASV_Cluster_ID, values_from = Count) %>% .[,5:69] %>% column_to_rownames("Sample")

Colon.wide.amp.md <- Counts.wide.md %>% rownames_to_column("Sample") %>% filter(grepl("COLON", Sample )) %>% filter(grepl("Ampicillin", Sample )) %>%
  column_to_rownames("Sample")
Colon.wide.van.md <- Counts.wide.md %>% rownames_to_column("Sample") %>% filter(grepl("COLON", Sample )) %>% filter(grepl("Vancomycin", Sample )) %>%
  column_to_rownames("Sample")
Colon.wide.water.md <- Counts.wide.md %>% rownames_to_column("Sample") %>% filter(grepl("COLON", Sample )) %>% filter(grepl("Water", Sample )) %>% 
  column_to_rownames("Sample")

permanova.Colon.amp <- adonis(Colon.wide.amp ~ Day, Colon.wide.amp.md)
permanova.Colon.van <- adonis(Colon.wide.van ~ Day, Colon.wide.van.md)
permanova.Colon.water <- adonis(Colon.wide.water ~ Day, Colon.wide.water.md)
permanova.Colon.amp$aov.tab
permanova.Colon.van$aov.tab
permanova.Colon.water$aov.tab
```


# Supplemental Figure 3: Beta diversity as recovery and keystone species 
```{r}
colours.tx <- c("#5884B4", "#E89A47", "#04955C")

long.0 <- Counts.wide %>% rownames_to_column("Sample") %>% pivot_longer(-Sample, names_to = "BugID", values_to = "Count") %>% filter(BugID == 2)
# now we have all the samples, with and without 121. 
long.0 <- long.0 %>% separate(Sample, c("Treatment", "Day", "Tissue", "Mouse", "Section", "FoV"), remove = FALSE)
#change order to be water amp vn
long.0$Treatment <- as.factor(long.0$Treatment) # make them as factors
long.0$Treatment <- factor(long.0$Treatment, levels=c('Water', 'Ampicillin', 'Vancomycin')) # change their order

# get beta diversity

# Within a tissue type and treatment, get the diversity difference between day -8 and day 35
ks <- All.BC.df.md %>% filter(Tissue.x == Tissue.y) %>% filter(Treatment.x == Treatment.y) %>% filter(Day.x == -8 , Day.y == 35)
# Var2 is what we are comparing to baseline

# add in baseline count of keystone species so match to Var1
baseline <- ks %>% left_join(long.0, by = c("Var1" = "Sample") )

recovery <- ks %>% left_join(long.0, by = c("Var2" = "Sample") )

baseline %>% ggplot(aes(x = Count, y = 1-BC)) + geom_point(aes(colour = Treatment), alpha = 0.2) + ggtitle("Baseline") + 
  geom_smooth(method = "lm", aes(colour = Treatment)) +
  ylab("Recovery (1-Bray Curtis)") +
  xlab("Duncaniella dubosii 4 abundance at baseline") +
  facet_grid(~Tissue, scales = "free") +
  stat_cor(method = "pearson", aes(colour = Treatment), label.x = 50  ) +
   scale_colour_manual(values=colours.tx)

# BOTH TISSUES
baseline %>%  ggplot(aes(x = Count, y = 1-BC)) + 
  geom_point(aes(colour = Treatment), alpha = 0.2) + 
  geom_smooth(method = "lm", aes(colour = Treatment)) +
  ylab("Recovery (1-Bray Curtis)") +
  xlab("C. scindens  abundance at baseline") +
  stat_cor(method = "pearson", aes(colour = Treatment), label.x = 550 ) +
   scale_colour_manual(values=colours.tx)
#ggsave("../Figures/Spatial/BugID_2_BaselineAbundance.pdf", width = 7, height = 5)
```

# Supplemental Figure 3 Cont'd
```{r}
long.0 <- Counts.wide %>% rownames_to_column("Sample") %>% pivot_longer(-Sample, names_to = "BugID", values_to = "Count") %>% filter(BugID == 2)
 # now we have all the samples, with and without 121. 
long.0 <- long.0 %>% separate(Sample, c("Treatment", "Day", "Tissue", "Mouse", "Section", "FoV"), remove = FALSE)
long.0$Day %>% unique() #all days are here


long.0$Treatment <- long.0$Treatment %>% as.factor() %>% factor(levels = c("Water", "Ampicillin", "Vancomycin"))
stats.cecum <- long.0 %>% filter(Day != 0, Tissue == "CECUM") %>% group_by(Treatment) %>% 
   rstatix::pairwise_wilcox_test(Count ~ Day, p.adjust.method = "BH") %>% add_xy_position(x = "Treatment")

stats.colon <- long.0 %>% filter(Day != 0, Tissue == "COLON") %>% group_by(Treatment) %>% 
   rstatix::pairwise_wilcox_test(Count ~ Day, p.adjust.method = "BH") %>% add_xy_position(x = "Treatment")

stats.BtoR <- long.0 %>% filter(Day != 0) %>% group_by(Treatment) %>% 
   rstatix::pairwise_wilcox_test(Count ~ Day, p.adjust.method = "BH") %>% add_xy_position(x = "Treatment")

# colours are
colours.days <- c("#F8766D",  "#619CFF")

long.0$Day <- gsub(pattern = "8", replacement = "-8", x =  long.0$Day)
long.0 %>% select(Tissue, Treatment, Day, Count) %>% filter(Day != 0) %>% 
ggplot(aes(x = Treatment, y = Count, colour = Day)) + geom_boxplot() +  scale_y_log10() + stat_pvalue_manual(stats.BtoR, y.position = 3, hide.ns = TRUE) + ggtitle("C. scindens abundance") +
  scale_colour_manual(values=colours.days)
#ggsave("../Figures/Spatial/Bug2Abundance.pdf", width = 5, height = 4)  

long.0 %>% select(Tissue, Treatment, Day, Count) %>% filter(Tissue == "CECUM", Day != 0) %>%
ggplot(aes(x = Treatment, y = Count, colour = Day)) + geom_boxplot() +  scale_y_log10() + stat_pvalue_manual(stats.cecum, y.position = 2.8, hide.ns = TRUE)
#ggsave("../Figures/Spatial/Bug121AbundanceCecum.pdf", width = 5, height = 4)   

long.0 %>% select(Tissue, Treatment, Day, Count) %>% filter(Tissue == "COLON", Day != 0) %>%
ggplot(aes(x = Treatment, y = Count, colour = Day)) + geom_boxplot() +  scale_y_log10() + stat_pvalue_manual(stats.colon, y.position = 2.8, hide.ns = TRUE)
#ggsave("../Figures/Spatial/Bug121AbundanceColon.pdf", width = 5, height = 4)     
```


